Poster Data Analysis

### 2018-10-03 notebooks/poster_analysis.Rmd
minor changes

# Description
This notebook presents the analysis of whole genome data for the poster "Quinolone resistance mechanisms found in E. coli from four animal species in Norway
", presented at the ASM NGS Conference in Washington D.C. September 2018.

@@

# Import data
This chunk imports data from MLST and ARIBA[1] AMR gene detection results. Isolate data is also imported.
Four isolates were excluded due to bad sequence quality.
```{r}
# Isolate data, including DNA extraction results, species,
# method of isolation, and sequencing methodology
isolate_data <- read.table("../data/isolate_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F) %>%
  filter(id %not_in% c("2016-02-428-2-S","2016-02-486-2-S","2016-02-732-2-S","2016-17-565-1-S"))

# Total MIC profile for all isolates in this study
mic_data <- read.table("../data/mic_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F) %>%
  filter(id %not_in% c("2016-02-428-2-S","2016-02-486-2-S","2016-02-732-2-S","2016-17-565-1-S"))

@@

# Arrange both plots into one figure
grid.arrange(arrangeGrob(p1 + theme(plot.margin=margin(51,-2,135,0)),
                         heights = c(1.9,-0.097)),
             arrangeGrob(p2 + theme(axis.text.y=element_blank(),
                                    plot.margin = margin(0,0,0,-8)),
                         heights=c(0.98,-0.03)), 
             ncol=2)

>>>>

# Description
This notebook presents the analysis of whole genome data for the poster "Quinolone resistance mechanisms found in E. coli from four animal species in Norway", presented at the ASM NGS Conference in Washington D.C. September 2018.

@@

# Import data
This chunk imports data from MLST and ARIBA[1] AMR gene detection results. Isolate data is also imported.
Four isolates were excluded due to bad sequence quality.
```{r}
# Isolate data, including DNA extraction results, species,
# method of isolation, and sequencing methodology
isolate_data <- read.table("../data/isolate_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)
  filter(id %not_in% c("2016-02-428-2-S","2016-02-486-2-S","2016-02-732-2-S","2016-17-565-1-S"))

# Total MIC profile for all isolates in this study
mic_data <- read.table("../data/mic_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

@@

# Arrange both plots into one figure
grid.arrange(arrangeGrob(p1 + theme(plot.margin=margin(51,-2,135,0)),
                         heights = c(1.9,-0.097)),
             arrangeGrob(p2 + theme(axis.text.y=element_blank(),
                                    plot.margin = margin(0,0,0,-8)),
                         heights=c(0.98,-0.03)), 
             ncol=2)
```
